%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins

\name{Cijo George} % Your name
%\address{B-301, Samvriddhi Gardenia Apartments} % Your address
%\address{Sahakar Nagar, Bangalore - 560092} % Your secondary addess (optional)
\address{{\bf Email:} cijogeorge.in@gmail.com, {\bf Phone:} +91 99 4567 0410}  
\address{{\bf LinkedIn}.com/in/cijogeorge, {\bf GitHub}.com/cijogeorge}

\begin{document}

%----------------------------------------------------------------------------------------
%	SUMMARY
%----------------------------------------------------------------------------------------

\begin{rSection}{Summary}

A Technology Leader with 10+ years of experience in Engineering, Research and Leadership roles across AI/ML and Platform Engineering, with a passion for building innovative technologies and high-performance teams. 

\end{rSection}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Indian Institute of Science (IISc)} \hfill {2010 - 2012} \\ 
{\em Supercomputer Education \& Research Centre} \smallskip \\
{\em Degree:} {\bf Master of Science in Engineering (Research)} \\
{\em Thesis:} Fault Tolerance Strategies for Large Scale Systems

{\bf Cochin University of Science \& Technology (CUSAT)} \hfill {2005 - 2009} \\
{\em Govt. Model Engineering College} \smallskip \\
{\em Degree:} {\bf Bachelor of Technology, Computer Science \& Engineering}

\end{rSection}

%----------------------------------------------------------------------------------------
%	EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Work Experience}

\begin{rSubsection}{Head of Platform \& AI}{Dec 2019 - Dec 2020}{Belong.co}{Bengaluru}
\item Responsible for building/ maintaining stable and scalable AI/ML and Platform Services for all SaaS products of Belong, serving enterprise customers in the recruitment domain.
\item Led a team of Researchers/ Data Scientists and Backend Engineers working on {\em Machine Learning/ Deep Learning} algorithms and scalable {\em API services} for {\em Contextual Candidate/ Job Search}, {\em Resume Parsing}, {\em Personalized Content Generation} and {\em Content Delivery}.
\item Led efforts to revamp Belong's {\em Resume Parsing} algorithm and service, making it scalable, with performance metrics at par with the best in the industry, ending dependence on paid third-party parsing services and enabling an additional revenue stream for the company.
\item Architected and developed (hands-on) a revamped version of  {\em Contextual Candidate/ Job Search} ranking algorithm, making it vertical/ domain agnostic, to  serve different job verticals in international markets.
\item Worked closely with Product Management to understand product requirements and influence product roadmap based on technology strategy and roadmap.

\end{rSubsection}

\begin{rSubsection}{Lead Data Scientist}{Jan 2019 - Nov 2020}{Belong.co}{Bengaluru}
\item Architected and developed (hands-on + leading the team) automated {\em feedback loops} that incorporate Candidate preferences learned from previous engagements into the core {\em Search Ranking} algorithm.
\item Led efforts in experimenting and building AI tools for a candidate facing product under development. 
\item Hired, on-boarded and mentored Researchers/ Data Scientists and Interns; and led campus recruitment efforts for tech hiring.
\end{rSubsection}

\begin{rSubsection}{Senior Data Scientist}{Feb 2018 - Dec 2018}{Belong.co}{Bengaluru}
\item Worked on improving the core recommendation system for Belong's flagship {\em Contextual People Search Engine} using techniques from across {\em Information Retrieval}, {\em Machine Learning}, {\em Deep Learning}, {\em Natural Language Processing} and {\em Statistical Analysis}.
\item Implemented, {\em A/B tested} and launched multiple incremental updates to the core {\em Search Ranking} algorithm with new signals, improving performance metrics by more than 50\%.  
\item Built the first version of {\em Belong Knowledge Graph}, powered by a scalable graph database, to capture relationships between Candidates, Skills,  Designations, Employers, Schools etc., enabling efficient Ad hoc complex queries across multiple dimensions for various use cases.

\end{rSubsection}

\begin{rSubsection}{Researcher (Advanced Technology Group, CTO Office)}{Aug 2012 - Jan 2018}{NetApp, Inc.}{Bengaluru}
\item Led advanced development projects with responsibility of studying the problem, proposing a solution, developing a working prototype/ proof-of-concept and taking prototypes into production.
\item Worked on applying classical {\em Machine Learning}, {\em Neural Networks} and {\em Time-series Analysis} ({\em Forecasting}, {\em Anomaly Detection}) on System Performance Metrics and Log data for various use cases.
\item Co-authored multiple peer-reviewed external publications, and several internal reports to influence long-term technology strategy of NetApp. 
\end{rSubsection}

\begin{rSubsection}{Software Engineer (R\&D)}{Jun 2009 - Jul 2010}{Nokia Siemens Networks}{Bengaluru}
\item Part of development team for {\em HLR (Home Location Register)}, a key component for call handling and value-added services in the telecommunications core network. Involved in feature development for the next generation {\em HLR} release versions as well as maintenance of older versions.

\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	PUBLICATION
%----------------------------------------------------------------------------------------

\begin{rSection}{External Publications}

\begin{rPubPatContList}
\item Rukma Talwadker, {\bf Cijo George}, ``Yodea: Workload Pattern Assessment Tool for Cloud Migration", {\em CloudCom '18: Proceedings of the 10th IEEE International Conference on Cloud Computing Technology and Science}, Nicosia, Cyprus, December 2018.
\item {\bf Cijo George}, Sathish Vadhiyar, ``Fault Tolerance on Large Scale Systems using Adaptive Process Replication", {\em IEEE Transactions on Computers}, September 2014.
\item Vipul Mathur, {\bf Cijo George}, Jayanta Basak, ``Anode: Empirical Detection of Performance Problems in Storage Systems using Time-Series Analysis of Periodic Measurements", {\em MSST '14: Proceedings of the 30th International Conference on Massive Storage Systems and Technology (IEEE)}, Santa Clara, California, June 2014.
\item {\bf Cijo George}, Sathish Vadhiyar, ``AdFT: An Adaptive Framework for Fault Tolerance on Large Scale Systems using Application Malleability", {\em ICCS '12: Proceedings of the International Conference on Computational Science (Elsevier)}, Omaha, Nebraska, June 2012.
\end{rPubPatContList}
   
\end{rSection}

%----------------------------------------------------------------------------------------
%       TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Familiar Techniques, Tools \& Tech Stack}

\begin{rTechExpertiseList}
\item {\bf Data Science}: Working knowledge of {\em Deep Learning}/ {\em Neural Networks} for {\em Natural Language Processing} ({\em Embeddings}, {\em Recurrent Models}, {\em Convolutional Models}, {\em Attention-based Models}, {\em Transformer-based Models}), {\em Gibbs Sampling}, {\em Latent Dirichlet Allocation}, {\em Hidden Markov Models}, {\em Page-Rank}, Classical Machine Learning ({\em Regression}, {\em Trees \& Forests}, {\em SVN}, {\em KNN}), {\em Time-series Analysis}.
\item{\bf Math}: Intuitive understanding of math behind familiar Data Science techniques.
\item {\bf Programming}: Most familiar with {\em Python}. Have worked with {\em Shell scripting}, {\em SQL}, {\em R}, {\em C}, {\em C++}, {\em MPI}, {\em CUDA}, {\em Perl}, {\em PHP}, {\em HTML}.
\item {\bf Tools \& Tech Stack}: Familiar with {\em Django}, {\em Celery}, {\em Jupyter}, {\em Git}, {\em Dgraph} (Graph Database), {\em Docker}, {\em Nginx}, {\em Gunicorn}, {\em Kubernetes}, {\em AWS}, {\em Hadoop} ({\em Hive}, {\em MapReduce}).
\item {\bf Others}: {\em RESTful API Design}, {\em Agile} Development, Working Knowledge of Operating Systems, Storage Systems and Networks.
\end{rTechExpertiseList}

\end{rSection}

%------------------------------------------------

%----------------------------------------------------------------------------------------
%	PATENTS
%----------------------------------------------------------------------------------------

%\begin{rSection}{Patents Filed}

%\begin{rPubPatContList}
%\item Vipul Mathur, {\bf Cijo George}, Swaminathan Ramany, {\em ``System and Method for Analyzing a Storage System for Performance Problems using Parametric Data"}, United States 14/194,467, Filed: February 28, 2014.
%\end{rPubPatContList}
   
%\end{rSection}

%----------------------------------------------------------------------------------------
%	AWARDS & RECOGNITION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Awards and Recognition}

%\begin{rAwardsContList}
%\item {\em CTO Awards} at NetApp - 2013, 2016.
%\item {\em Spot Awards} at NetApp - 2016, 2017.
%\item {\em Thank You} award for {\em Remarkable Contribution} at Nokia Networks - 2010.
%\end{rAwardsContList}
   
%\end{rSection}

%----------------------------------------------------------------------------------------
%	SOCIAL MEDIA
%----------------------------------------------------------------------------------------

%\begin{rSection}{Contact Details and Social Profiles}

%\begin{rPubPatContList}
%\item {\bf Email:} cijogeorge.in@gmail.com, {\bf Phone:} +91 99 4567 0410
%\item {\bf LinkedIn}.com/in/cijogeorge, {\bf GitHub}.com/cijogeorge
%\end{rPubPatContList}

%\end{rSection}

%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
